---
title: "yieldcurves"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{yieldcurves}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
author: "Henriette Elise Breymann, Gian-Andrin Tommasini"
date: "`r Sys.Date()`"
---
# Setup
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = FALSE}
library(FEMSdevPkg)
```
The following vignette is based on the vignette "linking" in the pkgdown package.
(Just an example on how we could include other vignettes in our vignettes.)
```{r, echo = FALSE}  
vignette("linking", package = "pkgdown")
# opens the vignette "linking" in the pkgdown package in browser
```

# Yield curves
Create a Yield curve object with the function `YieldCurve()`. The function takes the following arguments:
This is the valid case.
```{r}
ycID <- "yc001"
rd <- "2023-10-31"
tr <-  c(1.1, 2.0, 3.5 )/100
names(tr) <- c("1M", "1Y", "5Y")
dcc <- "30E360"
cf <- "NONE"
yc <- YieldCurve(ycID,rd,tr,dcc,cf)
# valid case
```

This is the invalid case.
```{r, error = TRUE}
dcc_e <- "30/360"
yc_e <- YieldCurve(ycID,rd,tr,dcc_e,cf)
# should generate error message for invalid dcc
# could also check for cf == "NONE" 
```

Now lets get the Forward rates for a given time period.
```{r}
Tfrom <- "2024-01-01"
Tto <- "2025-07-01"
frwdRate <- getForwardRates(yc, Tfrom,Tto)
frwdRate
```
The forward rate for the period from `r as.Date(Tfrom)` to `r as.Date(Tto)` is `r round(frwdRate, 4)`.
Now we would also want to see the discount rate or the growth factor. However, these functions are not public yet.

But we can see how the forward rate changes if we change the compounding frequency.
First we create new YieldCurve objects with different compounding frequencies.
```{r}
ycID <- "yc002"
rd <- "2023-10-31"
tr <-  c(1.1, 2.0, 3.5 )/100
names(tr) <- c("1M", "1Y", "5Y")
dcc <- "30E360"
cf <- "YEARLY"
yc2 <- YieldCurve(ycID,rd,tr,dcc,cf)

ycID <- "yc003"
rd <- "2023-10-31"
tr <-  c(1.1, 2.0, 3.5 )/100
names(tr) <- c("1M", "1Y", "5Y")
dcc <- "30E360"
cf <- "CONTINUOUS"
yc3 <- YieldCurve(ycID,rd,tr,dcc,cf)
```
Then we generate the forward rates for the same time period as before.
```{r}
frwdRate2 <- getForwardRates(yc2, Tfrom,Tto)
frwdRate3 <- getForwardRates(yc3, Tfrom,Tto)

frwdRate2
frwdRate3

```
The forward rate for the period from `r as.Date(Tfrom)` to `r as.Date(Tto)` is `r round(frwdRate2, 4)` with yearly compounding and `r round(frwdRate3, 4)` with continuous compounding.